The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-07 manuscript/manuscript.Rnw
discuss carmeli results

\begin{table}[h]
  \tiny
<<top.50.s.carmeli.expressed.genes,echo=FALSE,results="asis">>=
top.carmeli.genes <- top.genes.table(species.name="spalax carmeli")
print(xtable(top.carmeli.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.carmeli.genes,"Gene symbol")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Spalax carmeli}}
\label{tab:top50_s_carmeli_placenta}
\end{table}

The 50 non-housekeeping genes with highest expression (by \ac{FPKM})
in the term placenta of \textit{Spalax carmeli} are shown in
\cref{tab:top50_s_carmeli_placenta} with a list of all highly expressed
genes in Supplemental \cref{tab:all_spalax_carmeli_placenta}.

>>>>

\begin{table}[h]
  \tiny
<<top.50.s.carmeli.expressed.genes,echo=FALSE,results="asis">>=
top.carmeli.genes <- top.genes.table(species.name="spalax carmeli")
print(xtable(top.carmeli.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.carmeli.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\carmeli}{tab:all_spalax_carmeli_placenta}}
\label{tab:top50_s_carmeli_placenta}
\end{table}

The 50 non-housekeeping genes with highest expression (by \ac{FPKM})
in the term placenta of \carmeli are shown in
\cref{tab:top50_s_carmeli_placenta} with a list of all highly
expressed genes in Supplemental
\cref{tab:all_spalax_carmeli_placenta}. Numerous hemoglobin subunits
ware highly expressed
(\Sexpr{gene.expression("spalax_carmeli","Hbb-bh1",complete=TRUE)},
\Sexpr{gene.expression("spalax_carmeli","Hbb-a1",complete=TRUE)}, and
\Sexpr{gene.expression("spalax_carmeli","Hbb-bs",complete=TRUE)}), as
well as the relaxin
\Sexpr{gene.expression("spalax_carmeli","Rln1",complete=TRUE)},
multiple cathespins
(\Sexpr{gene.expression("spalax_carmeli","Ctsm",complete=TRUE)},
\Sexpr{gene.expression("spalax_carmeli","BC051665",complete=TRUE)},
and \Sexpr{gene.expression("spalax_carmeli","Ctsl",complete=TRUE)},
\cref{fig:cathespin_evolution_tree}), and many prolactin-related genes
(\Sexpr{gene.expression("spalax_carmeli","Prl4a1",complete=TRUE)},
\Sexpr{gene.expression("spalax_carmeli","Prl6a1",complete=TRUE)},
\Sexpr{gene.expression("spalax_carmeli","Prl3b1",complete=TRUE)}, and
\Sexpr{gene.expression("spalax_carmeli","Prl7c1",complete=TRUE)},
\cref{fig:prolactin_evolution_tree}) which shows a similar pattern of
expansion seen in \mouse.
